\chapter{State of the Art}
\label{sec:stateOfTheArt}

To get an idea of possible solutions and the most promising approaches, this chapter summarizes the most relevant state-of-the-art.
This chapter includes general information and task-specific projects focusing on the rail domain.
In \autoref{sec:networkArchitectures} describes the most relevant developments in network architectures.
Then, an introduction to different vision tasks and their approaches is given to serve as an overview in \autoref{sec:differentApproaches}.
Because three of those different vision tasks are relevant to this work, they are described in more detail.
\autoref{sec:ObjectDetection} depicts real-time object detectors, \autoref{sec:SemanticSegmentation} describes semantic segmentation approaches, and \autoref{sec:lineDetection} describes other approaches, which are summarized as line detection approaches.
\autoref{sec:transformerBasedApproaches} describes transformer-based approaches for object detection and segmentation tasks.
At one point in this work, \cite{tepNet2024} is selected as a baseline for further experiments.
Therefore, this project is explained in more detail in \autoref{sec:baselinepaper}.
Temporal model architectures are described in \autoref{sec:temporalModelArchitecture}.
\autoref{sec:datasets} thoroughly describes available datasets for the rail domain.

%%%%%%%%%%%%%%%%%%%%% network architectures %%%%%%%%%%%%%%%%%%%%%

\input{state_of_the_art/network_architectures.tex}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%% Different approaches of vision tasks %%%%%%%%%%%%%%%%%%%%%
\clearpage
\input{state_of_the_art/differentApproaches.tex}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%% Object Detection %%%%%%%%%%%%%%%%%%%%%

\input{state_of_the_art/ObjectDetection.tex}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%% Semantic Segmentation %%%%%%%%%%%%%%%%%%%%%

\clearpage 
\input{state_of_the_art/SemanticSegmentation.tex}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%% Transformer based appraoches %%%%%%%%%%%%%%%%%%%%%

\input{state_of_the_art/transformerBasedApproaches.tex}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%% Line Detection %%%%%%%%%%%%%%%%%%%%%

\clearpage                                                       % Beginne neue Seite
\input{state_of_the_art/line_detection}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%% Baseline Paper %%%%%%%%%%%%%%%%%%%%%

\clearpage                                                       % Beginne neue Seite
\input{state_of_the_art/Baseline.tex}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%% temporal network architectures %%%%%%%%%%%%%%%%%%%%%

\clearpage
\input{state_of_the_art/temporal_network_architectures.tex}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%% Datasets %%%%%%%%%%%%%%%%%%%%%

\clearpage                                                       % Beginne neue Seite
\input{state_of_the_art/Datasets.tex}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
