\section{Object detection Experiments}
\label{sec:objectDetectionExperiments}

The first approach pursued in this work is to combine an object detection model and a semantic segmentation model.
The semantic segmentation model should predict the track on a pixel level, and the object detection model predicts the direction of the train in scenarios where switches divide the track.

Experiments started with training object detection models from the \ac{YOLO} series.
The models \ac{YOLO}v7 \cite{yolov7} and \ac{YOLO}v9 \cite{YOLOv9} are selected to investigate their ability to predict switches and their states.
Experiments have been conducted with RailSem19 and subsets of this dataset, which are further described in \autoref{sec:usedDatasetsYOLOs}.
At the beginning of this work, \ac{YOLO}v9 was just released.
Consequently, not all models were fully supported during the experiments.
Therefore, the versions \ac{GELAN}-c and \ac{GELAN}-e are utilized.
For the \ac{YOLO}v7 the smallest version with the highest reported speed is used.
Many experiments are conducted with these three models, however only the best-performing are described.

When training \ac{YOLO} models, there is built-in data augmentation available.
This includes a horizontal flip of images.
Since this horizontal flip of images only flips images but does not change the label $switch\_left$ to $switch\_right$ and vice versa, this strategy cannot be used.
Consequently, the probability of such flips is defined to be zero. The remaining default data augmentation is utilized in all experiments.
Additionally, all other default hyperparameters are not changed, and parameters that are specified in the training command are used as they are recommended in the GitHub repositories \cite{YOLOv7GitHub} and \cite{YOLOv9GitHub}.
All changed and specified parameters of the best-performing experiments are shown in \autoref{tab:usedParametersYOLOs}.
Furthermore, all models come with pre-trained weights trained on the COCO dataset.
In all experiments, these weights are used as initialization.

\begin{table}[H]
    \centering
    \begin{tabular}{|l|c|c|}
    %\begin{tabular}{| p{0.3\linewidth} | p{0.6\linewidth} |}
        \hline
        \textbf{Parameters} & \textbf{YOLOv9 models} & \textbf{YOLOv7}\\
        \hline
        img\_size & $640 \times 640$ & $640 \times 640$ \\
        \hline
        epochs & $500$ & $500$\\
        \hline
        fliplr & $0.0$ & $0.0$\\
        \hline
        batch\_size& $16$ & $16$\\
        \hline
        workers & $8$ & $8$\\
        \hline
        min-items & $0$ & \\
        \hline
        close-mosaic & $15$ & \\
        \hline
    \end{tabular}
    \caption{Used parameters for training \ac{YOLO} object detection models}
    \label{tab:usedParametersYOLOs}
\end{table}